Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-06-18 tse19/main.tex
minor changes

To sum up, after obtaining the list of potential projects from GitHub,
we filtered those containing a \pomf{} file in the root
directory.\Comment{ A Maven project may contain several sub-modules
  with multiple \pomf{} files.}  Then, considering this set of Maven
projects, we executed the test suite for \SubjectsReruns{} times
discarding those projects with issues. Figure~\ref{fig:subjects}
shows the breakdown of projects by source of issue. As of
March 2019, our search returned a total of \SubjectsGithub{}
subjects.  We found that \SubjectsGithubNotMaven{}
projects in this set were not Maven. Compared with our previous
experiment~\cite{Candido:2017:TSP:3155562.3155667}, executed nearly 2
years ago, we observed  that many more
projects now use Gradle---73\% of the \SubjectsGithubNotMaven{} non-Maven
projects use Gradle. Although parallelization can
be used in Gradle, we decided to keep using using Maven for
consistency with the previous experiment. From the remaining set of
projects, \SubjectsGithubNotTestable{} were discarded
because of environment incompatibility (\eg, missing\Comment{ required
  web browser or database management system}~DBMS) and
\SubjectsGithubFlaky{} projects were discarded because of flaky
tests~\cite{luo-etal-fse2014}. A flaky test is a test that passes or
fails non-deterministically resulting in wasted effort.  As some of our experiments consist of running tests on
different threads, we ignored these projects as it would be
impractical to identify whether a test failed due to a race condition
or some other source of flakiness. Note that existing techniques exist to
detect and mitigate flakiness~\Fix{cite cite}, so we considered this
problem out of scope. From the remaining
\SubjectsGithubConsistant{} projects with test execution
manifesting deterministic results, we
eliminated \SubjectsGithubTooManyFailures{} projects that contain
\SuiteFailingThreshold{} or more failing tests as to reduce
bias. For projects with less failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to discard the failing tests as we did not
want a premature termination of test run to influence in timings.  Our final set of
subjects include  \numSubjs{} projects.

>>>>

To sum up, after obtaining the list of potential projects from GitHub,
we filtered those containing a \pomf{} file in the root
directory.\Comment{ A Maven project may contain several sub-modules
  with multiple \pomf{} files.}  Then, considering this set of Maven
projects, we executed the test suite for \SubjectsReruns{} times
discarding those projects with issues. Figure~\ref{fig:subjects}
shows the breakdown of projects by source of issue. As of
March 2019, our search returned a total of \SubjectsGithub{}
subjects.  We found that \SubjectsGithubNotMaven{}
projects in this set were not Maven. Compared with our previous
experiment~\cite{Candido:2017:TSP:3155562.3155667}, executed nearly 2
years ago, we observed  that many more
projects now use Gradle---73\% of the \SubjectsGithubNotMaven{} non-Maven
projects use Gradle. Although parallelization could
be used in Gradle, we decided to keep using Maven for
consistency with the previous experiment. From the remaining set of
projects, \SubjectsGithubNotTestable{} were discarded
because of environment incompatibility (\eg, missing\Comment{ required
  web browser or database management system}~DBMS) and
\SubjectsGithubFlaky{} projects were discarded because of flaky
tests~\cite{luo-etal-fse2014}. A flaky test is a test that passes or
fails non-deterministically resulting in wasted effort.  As some of our experiments consist of running tests on
different threads, we ignored these projects as it would be
impractical to identify whether a test failed due to a race condition
or some other source of flakiness. Note that existing techniques exist to
detect and mitigate flakiness~\Fix{cite cite}, so we considered this
problem out of scope. From the remaining
\SubjectsGithubConsistant{} projects with test execution
manifesting deterministic results, we
eliminated \SubjectsGithubTooManyFailures{} projects that contain
\SuiteFailingThreshold{} or more failing tests as to reduce
bias. For projects with fewer failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to discard the failing tests as we did not
want a premature termination of a test run to influence in time measurements.  Our final set of
subjects include  \numSubjs{} projects.
